Meritocracy and distributive preferences ISSP

### 2020-08-19 production/prod_analysis-a.rmd
update

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

**Libraries**
```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer) 
library(semTools)
library(plyr) # count
library(dplyr)
library(car) # recode
library(ggplot2)
library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter	
library(semPlot)
library(haven)
library(sjlabelled) 
library(kableExtra)
library(ggeffects)
library(influence.ME)
library(lattice)

@@

```{r}
load(file = "input/data/proc/redistrib.rda")
load(file="input/data/proc/mer_pref.rda")
	load("input/data/proc/redistrib.rda")
	load("input/data/proc/getahead.rda")                       
	load("input/data/proc/detearn.rda")

# Descriptives
```{r results='asis'}
  # Summary table to latex
    sink("output/results/desctab_red.html")
    stargazer(redistrib[-c(1,2)], type="html"); sink()
```

@@

    # cambiar orden para la leyenda  
    labels= c("Strongly agree", "Agree", "Disagree",
              "Strongly disagree", "(neither/nor)" )  ### E
    png<-sjPlot::plot_likert((redistrib[3:7]), 
                        axis.labels   = items,
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Redistribution preferences.",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )

    # Save
    ggsave(png,filename = "output/images/plotlikert.png",device = "png", width=10, height=5)

@@

```{r echo=FALSE}
     # short var labels

    # cambiar orden para la leyenda  
    labels= c("Strongly agree", "Agree", "Disagree",
              "Strongly disagree", "(neither/nor)" )  ### E
    png<-sjPlot::plot_likert((getahead[3:8]), 
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Get Ahead scale",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )

    # Save
    ggsave(png,filename = "output/images/plotlikert_getahead.png",device = "png", width=10, height=5)

@@

```{r echo=FALSE}
     # short var labels

    # cambiar orden para la leyenda  
    labels= c("Essential", "Very important", "Fairly important",
              "Not very important", "Not important at all" )  ### E
    png<-sjPlot::plot_likert((detearn[3:8]), 
                        legend.labels = labels,
                        cat.neutral = 3,
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Pay preferences",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )

    # Save
    ggsave(png,filename = "output/images/plotlikert_detearn.png",device = "png", width=10, height=5)

@@

# Modelos de medida {.tabset .tabset-fade .tabset-pills}

@@

	aux1 <- merge(getahead,redistrib,by=c("id","v5"))
  merit_redist=merge(aux1,detearn,by=c("id","v5"))

## Redistribution preferences.

```{r}
cfa_red1 <- '
	# latent variables
	redist =~ income_dif + unemployed + taxes 
	accum  =~ health + educ
	'
fit_mer_redis <- cfa(cfa_red1,data=merit_redist, 
	  	missing = "ML") 
#	 summary(fit_mer_red1, fit.measures=TRUE,standardized=TRUE)

fit_mer_redisc <- cfa(cfa_red1,data=merit_redist,
	  	ordered = names(merit_redist[3:10,19:23]))
	#	summary(fit_mer_redc, fit.measures=TRUE,standardized=TRUE)

fit_mer_redisc_group <- cfa(cfa_red1,data=merit_redist, group = "v5")
#summary(fit_mer_redisc_group, fit.measures=TRUE,standardized=TRUE)

sum_fit<- bind_rows(fitmeasures(fit_mer_redis)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_redisc)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],    
                    fitmeasures(fit_mer_redisc_group)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Meritocratic belief measurement model summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item",
                          "Model 3: multigroup"));sumtable01

  semPlot::semPaths(fit_mer_redis,layout = "tree", rotation = 3, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)

@@

# por paises   
merit_redist_arg<-  merit_redist %>% filter(v5==32)
fit_mer_redis_arg <- cfa(cfa_red1,data=merit_redist_arg,missing = "ML" , estimator="MLR")
merit_redist_australia<-  merit_redist %>% filter(v5==36)
fit_mer_redis_australia <- cfa(cfa_red1,data=merit_redist_australia,missing = "ML" , estimator="MLR")
merit_redist_austria<-  merit_redist %>% filter(v5==40)
fit_mer_redis_austria <- cfa(cfa_red1,data=merit_redist_austria,missing = "ML" , estimator="MLR")
merit_redist_belgium<-  merit_redist %>% filter(v5==56)
fit_mer_redis_belgium <- cfa(cfa_red1,data=merit_redist_belgium,missing = "ML" , estimator="MLR")
merit_redist_bulgaria<-  merit_redist %>% filter(v5==100)
fit_mer_redis_bulgaria <- cfa(cfa_red1,data=merit_redist_bulgaria,missing = "ML" , estimator="MLR")
merit_redist_chile<-  merit_redist %>% filter(v5==152)
fit_mer_redis_chile <- cfa(cfa_red1,data=merit_redist_chile,missing = "ML" , estimator="MLR")
merit_redist_china <-  merit_redist %>% filter(v5==156)
fit_mer_redis_china <- cfa(cfa_red1,data=merit_redist_china,missing = "ML" , estimator="MLR")
merit_redist_taiwan <-  merit_redist %>% filter(v5==158)
fit_mer_redis_taiwan <- cfa(cfa_red1,data=merit_redist_taiwan,missing = "ML" , estimator="MLR")
merit_redist_croatia <-  merit_redist %>% filter(v5==191)
fit_mer_redis_croatia <- cfa(cfa_red1,data=merit_redist_croatia,missing = "ML" , estimator="MLR")

@@

@@

fit_mer_redis_deutschland <- cfa(cfa_red1,data=merit_redist_deutschland,missing = "ML" , estimator="MLR")

@@

fit_mer_redis_nuevazelanda <- cfa(cfa_red1,data=merit_redist_nuevazelanda,missing = "ML" , estimator="MLR")

@@

@@

@@

@@

fit_mer_redis_estadosunidos <- cfa(cfa_red1,data=merit_redist_estadosunidos,missing = "ML" , estimator="MLR")

@@

#merit_redist_venezuela<-  merit_redist %>% filter(v5==862)
#fit_mer_redis_venezuela <- cfa(cfa_red1,data=merit_redist_venezuela,ordered = names(merit_redist[3:10,19:23]))

@@

sum_fit$mod <- c("Argentina","Australia","Austria", "Belguim","Bulgaria","Chile","China","Taiwan", "Croatia", "Chequia","Dinamarca","EST","Finlandia","Francia","Deutschland", "Islandia", "Israel","Italia", "Japon", "Letonia","Lituania","Nueva Zelanda", "Noruega", "Filipinas", "Polonia", "Rusia","Eslovequia","Eslovenia","Sudafrica", "España","Suecia","Suiza","Truquia","Ucrania","Reino Unido", "Estados Unidos.")

colnames <- c("Model","$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")
	  sum_fit <- sum_fit %>% dplyr::select("mod","chisq","df","cfi.robust","rmsea.robust","rmsea.ci.lower.robust","rmsea.ci.upper.robust")
sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit  countries",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle");sumtable01

@@

@@

## Meritocratic beliefs 
```{r}

	  cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	    '

fit_mer_mer <- cfa(cfa_perpref2,data=merit_redist, 
	  	missing = "ML") 
#	 summary(fit_mer_red1, fit.measures=TRUE,standardized=TRUE)

fit_mer_merc <- cfa(cfa_perpref2,data=merit_redist,
	  	ordered = names(merit_redist[3:10,19:23]))
	#	summary(fit_mer_redc, fit.measures=TRUE,standardized=TRUE)

fit_mer_mer_group <- cfa(cfa_perpref2,data=merit_redist, group = "v5")
#summary(fit_mer_redisc_group, fit.measures=TRUE,standardized=TRUE)

sum_fit<- bind_rows(fitmeasures(fit_mer_mer)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_merc)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],    
                    fitmeasures(fit_mer_mer_group)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Redistribution measurement model summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item",
                          "Model 3: multigroup"));sumtable01

  semPlot::semPaths(fit_mer_mer,layout = "tree", rotation = 3, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)
```

@@

@@

sum_fit$mod <- c("Argentina","Australia","Austria", "Belguim","Bulgaria","Chile","China","Taiwan", "Chequia","Dinamarca","EST","Finlandia","Francia","Deutschland", "Venezuela#", "Islandia", "Israel", "Japon","Lituania","Nueva Zelanda", "Noruega", "Filipinas", "Polonia", "Rusia","Eslovequia","Eslovenia","Sudafrica", "España","Suecia","Suiza","Truquia","Ucrania","Reino Unido", "Estados Unidos.")
colnames <- c("Model","$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")
	  sum_fit <- sum_fit %>% dplyr::select("mod","chisq","df","cfi.robust","rmsea.robust","rmsea.ci.lower.robust","rmsea.ci.upper.robust")
sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit country",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle");sumtable01

@@

El modelo no converge ni en croatia, Chipre, Italia ni Letonia

## Meritocracy and Redistribution.  
```{r}

	# CFA with secon order unmerit

	  cfa_mer_red2 <- '
	  # latent variables
		  merit =~ hwork + ambition 
		  parent=~ wealthy + pareduc
		  backg=~ race + gender
			network=~ people + polcone
		  bmerit =~ welljob + hardjob 
		  need=~ family + child
			redist =~ income_dif + unemployed + taxes 
	  	accum  =~ health + educ
			unmerit =~ parent + backg + network
	  '     
	  fit_mer_red2 <- cfa(cfa_mer_red2,data=merit_redist, 
	  	missing = "ML") 
#	 summary(fit_mer_red1, fit.measures=TRUE,standardized=TRUE)

	  fit_mer_red2c <- cfa(cfa_mer_red2,data=merit_redist,
	  	ordered = names(merit_redist[3:10,19:29]))
	#	summary(fit_mer_redc, fit.measures=TRUE,standardized=TRUE)

sum_fit<- bind_rows(fitmeasures(fit_mer_red2)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_red2c)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])
sum_fit$mod <- c("Model 1","Model 2")
sum_fit$est <- c("MLR","DWLS")
sum_fit <- sum_fit %>% dplyr::select("mod","est","chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")

@@

@@

	    # Correlations
	  cormat=cor(fscores[c(7,8,1,9,5,6)],
	             use="pairwise.complete.obs")

@@

		dev.off()

@@

## Macro level corr

@@

#Se agrega la base de datos dejando paises como
  mer_pref_agg=aggregate(mer_pref, by=list(mer_pref$v5c),
    	FUN=mean, na.rm=TRUE)
      names(mer_pref_agg)[names(mer_pref_agg)=="Group.1"]="v5c"

@@

  # Adjust data
    merit_agg=aggregate(meritocracy, by=list(meritocracy$v5c),
    	FUN=mean, na.rm=TRUE)
    names(merit_agg)[names(merit_agg)=="Group.1"]="v5c"
 #   names(merit_agg)
  #  dim(merit_agg)

@@

	corrplot(
corMat,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A", 
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)

	dev.off()

@@

```{r results='hide'}
plotredistgini<-plot_scatter(mer_pref_agg, gini_neto, redist, 
    title = "Redistribution and inequality",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()  + ylab("Redistribution preferences") + xlab("Gini index")

plotredistgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, redist, 
	    	title = "Redistribution and inequality (without outliers)",
    	 fit.line = lm,
	    	show.ci = TRUE
		   	) + theme_classic() + ylab("Redistribution preferences") + xlab("Gini index")

plotredistfi<-plot_scatter(mer_pref_agg,  fi_index, redist, 
    title = "Redistribution and Economic freedom index",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Redistribution preferences") + xlab("Economic freedom index")

plotredistfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, redist, 
    title = "Redistribution and Economic freedom index (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Redistribution preferences") + xlab("Economic freedom index")

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

**Libraries**
```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer) 
library(semTools)
library(plyr) # count
library(dplyr)
library(car) # recode
library(ggplot2)
library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter	
library(semPlot)
library(haven)
library(sjlabelled) 
library(kableExtra)
library(ggeffects)
library(influence.ME)
library(lattice)
```

@@

```{r}
load(file = "input/data/proc/redistrib.rda")
load(file = "input/data/proc/mer_pref.rda")
load("input/data/proc/redistrib.rda")
load("input/data/proc/getahead.rda")
load("input/data/proc/detearn.rda")
```

# Descriptives
```{r results='asis'}
# Summary table to latex
sink("output/results/desctab_red.html")
stargazer(redistrib[-c(1, 2)], type = "html")
sink()
```

```{r}
set_theme(base = theme_bw(),
          theme.font = "serif", 
          axis.textsize.x = 1.2,
          axis.textsize.y = 1.2, 
          geom.label.size = 4, 
          legend.just = 0.35, 
          legend.size = 1.2,
          legend.backgroundcol = "white")
```

@@

# cambiar orden para la leyenda  
labels= c("Strongly agree", "Agree", "Disagree",
          "Strongly disagree", "(neither/nor)" )  ### E
png<-sjPlot::plot_likert((redistrib[3:7]), 
                         axis.labels   = items,
                         legend.labels = labels,
                         cat.neutral   = 5, # identifica a indiferentes
                         geom.colors   = c("#9ecae1", "#6baed6", "#4292c6",
                                           "#2171b5"), # colorbrewer2.org
                         sort.frq      = "neg.asc", # sort descending)
                         title         = "Redistribution preferences.",
                         intercept.line.color = "white", # vertical middle
                         expand.grid   = F, # no inner margins in plot
                         show.n        = FALSE, # hide N's in axis labels
                         grid.range    = 1.8,
                         geom.size = 0.6) # expand axis 130% )

ggsave(png,filename = "output/images/plotlikert.png",device = "png", width=15, height=5)
```

@@

```{r echo=FALSE}
# short var labels
# cambiar orden para la leyenda  
labels= c("Strongly agree", "Agree", "Disagree", "Strongly disagree", "(neither/nor)" )  ### E

png<-sjPlot::plot_likert((getahead[3:8]), 
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Get Ahead scale",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )

# Save
ggsave(png,filename = "output/images/plotlikert_getahead.png",device = "png", width=15, height=5)
```

@@

```{r echo=FALSE}
# short var labels
# cambiar orden para la leyenda  
labels= c("Essential", "Very important", "Fairly important",
              "Not very important", "Not important at all" )  ### E

png<-sjPlot::plot_likert((detearn[3:8]), 
                        legend.labels = labels,
                        cat.neutral = 3,
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Pay preferences",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )
# Save
ggsave(png,filename = "output/images/plotlikert_detearn.png",device = "png", width=15, height=5)
```

@@

# Measurement models {.tabset .tabset-fade .tabset-pills}

@@

aux1 <- merge(getahead, redistrib, by = c("id", "v5"))
merit_redist = merge(aux1, detearn, by = c("id", "v5"))
```

## Redistributive preferences.

```{r, cache=TRUE}
cfa_red1 <- '
	# latent variables
	redist =~ income_dif + unemployed + taxes
	accum  =~ health + educ
	'
#--- continous fit-----
fit_mer_redis <- cfa(cfa_red1,data=merit_redist,missing = "ML") 
#	 summary(fit_mer_red1, fit.measures=TRUE,standardized=TRUE)

#--- ordinal fit  -----	 		  
fit_mer_redisc <- cfa(cfa_red1,data=merit_redist,ordered = names(merit_redist[3:10,19:23]))
#	summary(fit_mer_redc, fit.measures=TRUE,standardized=TRUE)

#--- group    fit-----	 		  
fit_mer_redisc_group <- cfa(cfa_red1,data=merit_redist, group = "v5")
#summary(fit_mer_redisc_group, fit.measures=TRUE,standardized=TRUE)
```

```{r}
sum_fit<- bind_rows(fitmeasures(fit_mer_redis)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_redisc)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],    
                    fitmeasures(fit_mer_redisc_group)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])

sum_fit$mod <- c("Model 1","Model 2", "Model 3")
sum_fit$est <- c("ML","DWLS", "ML")
sum_fit <- sum_fit %>% dplyr::select("mod","est","chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, 
                   caption = "Meritocratic belief measurement model summary fit",
                   col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item",
                          "Model 3: Multigroup CFA"));sumtable01
```

```{r}
semPlot::semPaths(
  fit_mer_redis,
  layout = "tree",
  rotation = 3,
  intercepts = FALSE,
  style = "lisrel",
  curvePivot = TRUE,
  sizeMan = 4,
  sizeLat = 6)
```

@@

```{r, cache=TRUE}
# por paises   
merit_redist_arg        <- merit_redist %>% filter(v5 == 32)
fit_mer_redis_arg       <- cfa(cfa_red1,data=merit_redist_arg,missing = "ML" , estimator="MLR")
merit_redist_australia  <- merit_redist %>% filter(v5==36)
fit_mer_redis_australia <- cfa(cfa_red1,data=merit_redist_australia,missing = "ML" , estimator="MLR")
merit_redist_austria    <- merit_redist %>% filter(v5==40)
fit_mer_redis_austria   <- cfa(cfa_red1,data=merit_redist_austria,missing = "ML" , estimator="MLR")
merit_redist_belgium    <- merit_redist %>% filter(v5==56)
fit_mer_redis_belgium   <- cfa(cfa_red1,data=merit_redist_belgium,missing = "ML" , estimator="MLR")
merit_redist_bulgaria   <- merit_redist %>% filter(v5==100)
fit_mer_redis_bulgaria  <- cfa(cfa_red1,data=merit_redist_bulgaria,missing = "ML" , estimator="MLR")
merit_redist_chile      <- merit_redist %>% filter(v5==152)
fit_mer_redis_chile     <- cfa(cfa_red1,data=merit_redist_chile,missing = "ML" , estimator="MLR")
merit_redist_china      <- merit_redist %>% filter(v5==156)
fit_mer_redis_china     <- cfa(cfa_red1,data=merit_redist_china,missing = "ML" , estimator="MLR")
merit_redist_taiwan     <- merit_redist %>% filter(v5==158)
fit_mer_redis_taiwan    <- cfa(cfa_red1,data=merit_redist_taiwan,missing = "ML" , estimator="MLR")
merit_redist_croatia    <- merit_redist %>% filter(v5==191)
fit_mer_redis_croatia   <- cfa(cfa_red1,data=merit_redist_croatia,missing = "ML" , estimator="MLR")

@@

merit_redist_chequia     <- merit_redist %>% filter(v5 == 203)

@@

fit_mer_redis_deutschland<- cfa(cfa_red1,data=merit_redist_deutschland,missing = "ML" , estimator="MLR")

@@

merit_redist_nuevazelanda<-  merit_redist %>% filter(v5==554)
fit_mer_redis_nuevazelanda<- cfa(cfa_red1,data=merit_redist_nuevazelanda,missing = "ML" , estimator="MLR")

@@

merit_redist_turquia     <-  merit_redist %>% filter(v5==792)

@@

merit_redist_ucrania     <-  merit_redist %>% filter(v5==804)

@@

merit_redist_reinounido  <-  merit_redist %>% filter(v5==826)

@@

fit_mer_redis_estadosunidos<- cfa(cfa_red1,data=merit_redist_estadosunidos,missing = "ML" , estimator="MLR")

@@

#merit_redist_venezuela<-  merit_redist %>% filter(v5==862)
#fit_mer_redis_venezuela <- cfa(cfa_red1,data=merit_redist_venezuela,ordered = names(merit_redist[3:10,19:23]))
```

@@

@@

```{r}
sum_fit$mod <- c("Argentina","Australia","Austria", "Belguim","Bulgaria","Chile","China","Taiwan", "Croatia", "Chequia","Dinamarca","EST","Finlandia","Francia","Deutschland", "Islandia", "Israel","Italia", "Japon", "Letonia","Lituania","Nueva Zelanda", "Noruega", "Filipinas", "Polonia", "Rusia","Eslovequia","Eslovenia","Sudafrica", "España","Suecia","Suiza","Truquia","Ucrania","Reino Unido", "Estados Unidos.")

colnames <- c("Model","$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")
sum_fit <- sum_fit %>% dplyr::select("mod","chisq","df","cfi.robust","rmsea.robust","rmsea.ci.lower.robust","rmsea.ci.upper.robust")
sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit  countries",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
  collapse_rows(columns = 1,valign = "middle");sumtable01
```

@@

## Meritocratic beliefs

```{r, cache=TRUE}
cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	    '
#--- continous fit-----
fit_mer_mer <- cfa(cfa_perpref2,data=merit_redist,missing = "ML") 
#	 summary(fit_mer_red1, fit.measures=TRUE,standardized=TRUE)

#--- ordinal fit  -----	 	
fit_mer_merc <- cfa(cfa_perpref2,data=merit_redist,ordered = names(merit_redist[3:10,19:23]))
#	summary(fit_mer_redc, fit.measures=TRUE,standardized=TRUE)

#--- group    fit-----
fit_mer_mer_group <- cfa(cfa_perpref2,data=merit_redist, group = "v5")
#summary(fit_mer_redisc_group, fit.measures=TRUE,standardized=TRUE)
```

```{r}
sum_fit<- bind_rows(fitmeasures(fit_mer_mer)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_merc)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],    
                    fitmeasures(fit_mer_mer_group)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Redistribution measurement model summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item",
                          "Model 3: multigroup"));sumtable01
```

```{r}
semPlot::semPaths(fit_mer_mer, layout = "tree", rotation = 3, intercepts = FALSE, style = "lisrel", curvePivot = TRUE, sizeMan = 4,  sizeLat = 6)
```

@@

```{r, cache=TRUE}

@@

@@

```{r}
sum_fit$mod <- c("Argentina","Australia","Austria", "Belguim","Bulgaria","Chile","China","Taiwan", "Chequia","Dinamarca","EST","Finlandia","Francia","Deutschland", "Venezuela#", "Islandia", "Israel", "Japon","Lituania","Nueva Zelanda", "Noruega", "Filipinas", "Polonia", "Rusia","Eslovequia","Eslovenia","Sudafrica", "España","Suecia","Suiza","Truquia","Ucrania","Reino Unido", "Estados Unidos.")
colnames <- c("Model","$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")
	  sum_fit <- sum_fit %>% dplyr::select("mod","chisq","df","cfi.robust","rmsea.robust","rmsea.ci.lower.robust","rmsea.ci.upper.robust")
sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit country",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle");sumtable01
```

**El modelo no converge ni en croatia, Chipre, Italia ni Letonia**

## Meritocracy and Redistribution.

```{r, cache=TRUE}
# CFA with secon order unmerit
cfa_mer_red2 <- '
	  # latent variables
		  merit =~ hwork + ambition 
		  parent=~ wealthy + pareduc
		  backg=~ race + gender
			network=~ people + polcone
		  bmerit =~ welljob + hardjob 
		  need=~ family + child
			redist =~ income_dif + unemployed + taxes 
	  	accum  =~ health + educ
			unmerit =~ parent + backg + network
	  '     
fit_mer_red2 <- cfa(cfa_mer_red2,data=merit_redist, missing = "ML") 
#	 summary(fit_mer_red1, fit.measures=TRUE,standardized=TRUE)
fit_mer_red2c <- cfa(cfa_mer_red2,data=merit_redist,ordered = names(merit_redist[3:10,19:29]))
#	summary(fit_mer_redc, fit.measures=TRUE,standardized=TRUE)
sum_fit<- bind_rows(fitmeasures(fit_mer_red2)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_red2c)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])

sum_fit$mod <- c("Model 1","Model 2")
sum_fit$est <- c("MLR","DWLS")
sum_fit <- sum_fit %>% dplyr::select("mod","est","chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")

@@

```{r}
sum_fit$mod <- c("Model 1","Model 2")
sum_fit$est <- c("MLR","DWLS")
sum_fit <- sum_fit %>% dplyr::select("mod","est","chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")

```{r}
semPlot::semPaths(fit_mer_red2,layout = "circle", rotation = 3, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)
```

@@

# Correlations
cormat=cor(fscores[c(7,8,1,9,5,6)],use="pairwise.complete.obs")

@@

dev.off()
```

@@

## Macro level correlation

@@

#Se agrega la base de datos dejando paises como
mer_pref_agg = aggregate(mer_pref,
                         by = list(mer_pref$v5c),
                         FUN = mean,
                         na.rm = TRUE)
names(mer_pref_agg)[names(mer_pref_agg) == "Group.1"] = "v5c"

@@

# Adjust data
merit_agg=aggregate(meritocracy, by=list(meritocracy$v5c),FUN=mean, na.rm=TRUE)
names(merit_agg)[names(merit_agg)=="Group.1"]="v5c"
#   names(merit_agg)
#  dim(merit_agg)

@@

corrplot(
corMat,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A", 
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)
dev.off()
```

@@

```{r}
set_theme(base = theme_classic(),
          theme.font = "serif", 
          axis.textsize.x = 1.2,
          axis.textsize.y = 1.2, 
          geom.label.size = 4, 
          legend.just = 0.35, 
          legend.size = 1.2,
          legend.backgroundcol = "white")

old <- theme_set(theme_classic())
theme_update(plot.caption = element_text(size = 12),
             text=element_text(size=12,  family="serif"))
```

```{r results='hide'}
plotredistgini <- plot_scatter(mer_pref_agg, gini_neto, redist,
                               title = "Redistribution and Inequality",
                             #dot.labels = merit_agg$v5c,
                             fit.line = "lm", 
                             show.ci = TRUE)  + ylab("Redistributive preferences") + xlab("Gini index")

mer_pref_agg_zaf <- mer_pref_agg[which(mer_pref_agg$v5c != 'ZAF'),]

plotredistgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, redist, 
                                        title = "Redistribution and inequality ",
                                        fit.line = lm,
                                        show.ci = TRUE) + ylab("Redistributive preferences") +xlab("Gini index") + labs(caption = "Excluding outliers")

plotredistfi <- plot_scatter(mer_pref_agg,  fi_index, redist,
                             title = "Redistribution and Economic Freedom Index",
                           #dot.labels = merit_agg$v5c,
                           fit.line = "lm",
                           show.ci = TRUE) +  ylab("Redistributive preferences") + xlab("Economic freedom index")

mer_pref_agg_ven <- mer_pref_agg[which(mer_pref_agg$v5c != 'VEN'),]
